Mimicry in Online Conversations: An Exploratory Study of Linguistic Analysis Techniques

### 2016-05-11 papers/asonam2016/short.tex
Few more experiments

\begin{table}[!t]
\caption{Correlations of Classifier Scores and Techniques}
\label{scores_techniques}
\centering
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l c c}
Layer, Technique & r & p \\
\hline
Lexical, LILLA & 0.27 & 0.005 \\
Syntactic, SILLA & 0.19 & 0.057 \\
Semantic, Word2vec & 0.11 & 0.231 \\
Lexical, LSM & 0.14 & 0.158 \\
Syntactic, LSM & 0.31 & 0.002 \\
Semantic, LSM & -0.13 & 0.202 \\
N/A (mean scores), LSM & 0.16 & 0.111
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\caption{Correlations of Techniques}
\label{techniques}
\centering
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l c c}
Technique & r & p \\
\hline
LILLA, SILLA & 0.26 & 0.007 \\
LILLA, Word2vec & -0.31 & 0.002 \\
SILLA, Word2vec & -0.81 & < 0.001
\end{tabular}
\end{table}

@@

More work is especially required to find if word vectors or related techniques can be used to find semantic mimicry with different methodology than ours, perhaps by parsing the text differently, running the measure on all utterances of each pair, rather than averaging the similarity over each pair of messages. More research in general is suggested in finding ways to capture mimicry at the semantic layer, and so far there is very little work looking at alignment at the situation layer.

>>>>

\begin{table}[!t]
\caption{Correlations of Classifier Scores and Techniques}
\label{scores_techniques}
\centering
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l c c}
Layer, Technique & r & p \\
\hline
Lexical, LILLA & 0.27 & 0.005 \\
Syntactic, SILLA & 0.19 & 0.057 \\
Semantic, Word2vec & 0.13 & 0.178 \\
Lexical, LSM & 0.14 & 0.158 \\
Syntactic, LSM & 0.31 & 0.002 \\
Semantic, LSM & -0.13 & 0.202 \\
N/A (mean scores), LSM & 0.16 & 0.111
\end{tabular}
\end{table}

@@

\begin{table}[!t]
\caption{Correlations of Techniques}
\label{techniques}
\centering
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l c c}
Technique & r & p \\
\hline
LILLA, SILLA & 0.26 & 0.007 \\
LILLA, Word2vec & -0.30 & 0.005 \\
SILLA, Word2vec & -0.82 & < 0.001
\end{tabular}
\end{table}

@@

More work is especially required to find if word vectors or related techniques can be used to find semantic mimicry with different methodology than ours, perhaps by parsing the text differently or experimenting with different models. More research in general is suggested in finding ways to capture mimicry at the semantic layer, and so far there is very little work looking at alignment at the situation layer.
